A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-12 pilot-publication/lab-book.Rmd
More work on comparing directly observed and retrospective data

>>>>

## Compare directly observed with retrospective data

```{r}
## Import data
data <- readr::read_csv(Sys.getenv("DATA_DIR"))

## Import codebook
codebook.arguments <- lapply(
    c("URL", "UID", "USERNAME", "PASSWORD"),
    function(x) Sys.getenv(paste0("KOBO_", x))
)
codebook <- do.call(noacsr::kobo_get_project_codebook, codebook.arguments)

## Prepare data
data <- prepare_data(data, codebook)

## Get variables to compare
retrospective.variables <- names(data)[grep("_r__", names(data), fixed = TRUE)]
directly.observed.variables <- retrospective.variables %>%
    stringr::str_replace_all(pattern = "\\_r\\_\\_", replacement = "\\_\\_") %>%
    stringr::str_replace_all(pattern = "\\_r$", replacement = "")

## Keep only observations with any retrospective data
data <- data[apply(data[, retrospective.variables], 1, function(row) any(!is.na(row))), ] %>%
    as_tibble()

## Extract retrospective and directly observed data
retrospective.data <- data[, retrospective.variables]
colnames(retrospective.data) <- directly.observed.variables
directly.observed.data <- data[, directly.observed.variables]
retrospective.data$collection.mode <- "Retrospective"
directly.observed.data$collection.mode <- "Directly observed"
original.classes <- sapply(directly.observed.data, class)

## Merge datasets
directly.observed.data[] <- lapply(directly.observed.data, as.character)
retrospective.data[] <- lapply(retrospective.data, as.character)
merged.data <- bind_rows(directly.observed.data, retrospective.data)

## Change column classes to match original classes
merged.data[] <- mapply(function(column, class.name) {
    class.function <- paste0("as.", class.name[1])
    new.column <- match.fun(class.function)(column)
    return(new.column)
}, merged.data, original.classes, SIMPLIFY = FALSE)
})

## Create table 
table.variables <- c(
    "patinfo__pt_age", "patinfo__pt_gender",
    "incident__dominating_injury_type",
    "patvitals__ed_rr", "patvitals__ed_sat",
    "patvitals__ed_hr", "patvitals__ed_sbp","outcomes__alive_after_30_days", 
    "collection.mode"
)
table.data <- merged.data[, table.variables]
comparison.table <- create_descriptive_table(table.data,
    strata = "collection.mode")
```
